Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records

### 2025-01-31 MANUSCRIPT.qmd
submission version

>>>>

## Open Research

All code and data necessary to reproduce the analyses presented in this manuscript are available at: <https://github.com/CaelumMroczek/baseflow-AZ>.

## Acknowledgements

The authors would like to express gratitude to the following people for helpful discussion and suggestions: Cole Denver, Aidan Houlgate, Rayni Lewis, Ryan Lima, Quentin McCalla, Isaiah Mesa, Georgia Roberts. This research was supported by an Arizona Board of Regents’ Grant from the Technology and Research Initiative Fund governed by A.R.S. § 15-1648. The authors acknowledge the financial support provided by this grant, which made this study possible.
